Type-Safe Modular Parsing

### 2017-01-14 paper/sections/Discussion.tex
A paragraph in 3.4 for ambiguity
Fix

The use of inheritance-based approach and Object Algebras enables us
to build modular parsers, which are able to evolve with together with
syntax. This section explores more interesting features, including
parsing multi-sorted syntax, overriding existing parsing rules,
language components for abstracting language features, and alternative
techniques under the whole framework.

@@

Using Object Algebras is that it is easy to
model multi-sorted languages. If the syntax contains multiple sorts, we can distinguish them by different type parameters. As an example, we extend the language of literals, additions and variables by introducing types as a new kind of type argument, and we add lambda abstractions to expressions. Now the language has two sorts in the syntax, types and expressions:\\

@@

\subsection{Overriding Existing Rules}

As many syntactically extensible parsers, our approach also supports
changing part of existing parsers, but in a type-safe way. We can
easily update existing parsing rules with new implementations, or
eliminate them in extended parsers. This can be useful in many
situations, including when conflicts or ambiguities arize when
composing languages.
As an illustration, suppose we have an untyped lambda abstraction case in a base parser as below. \inlinecode{pLam} parses a lambda symbol, an identifier, a dot and an expression in sequence. Some irrelevant details are omitted.

@@

As shown below, those two language components can be merged into one to obtain the language we want. Furthermore, the new language is still a modular
component ready for future composition. In that case modularity is realized over higher-order hierarchies.

@@

Besides Object Algebras, many other techniques including \textit{Data
  types à la carte} (DTC)~\cite{swierstra2008data} ot the Cake pattern~\cite{odersky2005independently} also support extensible data structures. These alternatives could also be adopted to build ASTs and corresponding parsers.

>>>>

The use of inheritance-based approach and Object Algebras enables us
to build modular parsers, which are able to evolve with
syntax together. This section explores more interesting features, including
parsing multi-sorted syntax, overriding existing parsing rules,
language components for abstracting language features, and alternative
techniques under the whole framework.

@@

Using Object Algebras, it is easy to
model multi-sorted languages. If the syntax contains multiple sorts, we can distinguish them by different type parameters. As an example, we extend the language of literals, additions and variables by introducing types, including primitive type \inlinecode{int} and function (arrow) type, and we add lambda abstractions to expressions. Now the language has two sorts in the syntax, types and expressions:\\

@@

\subsection{Overriding Existing Rules}\label{subsec:overriding-rules}

As many syntactically extensible parsers, our approach also supports
modifying part of existing parsers, but in a type-safe way. We can
easily update existing parsing rules with new implementations, or
eliminate them in extended parsers. This can be useful in many
situations, including when conflicts or ambiguities arize when
composing languages.
As an illustration, suppose we have an untyped lambda abstraction case in a base parser as below. \inlinecode{pLam} parses a lambda symbol, an identifier, a dot and an expression in sequence. Some irrelevant details are omitted.

@@

As shown in Figure~\ref{fig:compose-components}, those two language components can be merged into one to obtain the language we want. Furthermore, the new language is still a modular
component ready for future composition. In that case modularity is realized over higher-order hierarchies.

@@

Besides Object Algebras, many other techniques including \textit{Data
  types à la carte} (DTC)~\cite{swierstra2008data} and the Cake pattern~\cite{odersky2005independently} also support extensible data structures. These alternatives could also be adopted to build ASTs and corresponding parsers.
